### 2016-01-26 project/paper/appendices/productivity.tex
Conclusion en results.
typfouten verbeterd

Apart from university rankings and popularity measures, work productivity seems like a reasonable feature to use in order to assess eligibility to receive an award. We reason that hard work will more likely result in making some scientific breakthrough, which increases the chances of someone winning a Nobel Prize. The productivity feature is not trivial to define, however. Furthermore, even if we can define it, all information needed to compute it has to be available for as many training and testing instances as possible. We therefore view all examples as \emph{persons} rather than \emph{scientists} or \emph{politicians}, having certain properties. How we define the work productivity property is the only difference between both datasets. For scientists, the number of publications seems like a decent way of measuring how productive they've been. For politicians, the most resemblant feature would have been the number of legislations they managed to get accepted. This information isn't publicly available, however, so we looked at something else. Coming straight from the ToE knowledge base, the number of speeches at european parliament seemed a good proxy measure. Both are numeric properties which we can normalise to $[0, 100]$.

@@

>>>>

Apart from university rankings and popularity measures, work productivity seems like a reasonable feature to use in order to assess eligibility to receive an award. We reason that hard work will more likely result in making some scientific breakthrough, which increases the chances of someone winning a Nobel Prize. The productivity feature is not trivial to define, however. Furthermore, even if we can define it, all information needed to compute it has to be available for as many training and testing instances as possible. We therefore view all examples as \emph{persons} rather than \emph{scientists} or \emph{politicians}, having certain properties. How we define the work productivity property is the only difference between both datasets. For scientists, the number of publications seems like a decent way of measuring how productive they've been. For politicians, the most resemblant feature would have been the number of legislations they managed to get accepted. This information isn't publicly available, however, so we looked at something else. Coming straight from the ToE knowledge base, the number of speeches at the European Parliament seemed a good proxy measure. Both are numeric properties which we can normalise to $[0, 100]$.

@@

\subsection{Additional note}
After experiments, the productivity feature didn't seem to perform well in building a model and it was therefore excluded. The discussion whether it could be used if it were a good feature, however, is still interesting.
